%
%to crop the pdf, use
% pdfcrop --margins '0 50 0 50' figlayered.pdf figlayered2.pdf
% 


\NeedsTeXFormat{LaTeX2e}
%
%\documentclass[aps,pra,showpacs,amsmath,amssymb,superscriptaddress,nofootinbib]{revtex4}
\documentclass[]{article}
\usepackage{graphicx}% Include figure files
\usepackage{bm}% bold math
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{color}
\usepackage{soul}
\usepackage{nopageno}
\usepackage{tikz}
%%

\begin{document}  

\thispagestyle{empty}

\section{Corrections to proofs tol5002}

\begin{itemize}
    % \item {\color{red} cover page:  add Guigay's ORCID}
    \item line 108 missing the ``l" in ``external" in the URL:  https://github.com/oasys-kit/xoppy\_external\_codes/tree/master/src/INPRO
    \item line 174: remove the italics in {\it define}
    \item line 196 in equation (5) there is a tilde character in  $...=\exp(i\\textbf{k}_0 . \textbf{r})$ that must be removed.
    \item line 197 also in equation (5), there is a wrong subindex $k$ that should be $h$: $.... [2i \textbf{k}_h$
    \item line 269 $...=\exp(iu_s s)$ should be $...=\exp(iu_0 s)$
    \item line 281,  in footnote 1 should say ...in equation (9) [instead of equation (10)]
    \item line 282,  in footnote 2 should say `` along $\hat{\textbf{s}}_0$" instead of ``along $s_0$"
    \item line 303. No, Appendix B should not be placed here. We understand that Appendix B is not called, it will be done at line 556.
    \item line 336 in the title, please use {\boldmath{$a$}} instead of \textbf{a}
    \item line 365 in equation (26) place parenthesis in $\sin(2\theta_B)$
    \item line 396 please place ($D_0(T),D_h(T)$) instead of [$D_0(T),D_h(T)$] because it is a vector and is delimited by (...)  [as shown in equation (30)]
    \item line 397 the same as before
    \item line 421 please replace $M(T_1+T_2)=M(T_1)M(T_2)$ by $M(T_1+T_2)=M(T_2)M(T_1)$ 
    \item line 448, 450 in equation (33). Please revert to our original manuscript and explicitly write in line 1: ``$\text{with the choice} \operatorname{Im}a<0$". Similarly for line 2: ``$\text{with the choice}\operatorname{Im}a>0$". This is a subtle detail that $\operatorname{Im} a$ cannot pass from negative to positive, but it must be chosen to be negative or positive.   
    \item line 459 Please use () instead of [] as discussed for line 396
    \item line 477 Please use () instead of [] as discussed for line 396
    \item line 479 a small detail: the equal sign in $=m_{22}$ is too long, it seems you use math character instead of text one
     \item line 556. At the beginning of this paragraph, just after equations (39) please add a sentence that calls Appendix B:  ``These solutions, as well as those for Laue in equations(34), can also be obtained by direct integration of the TT equations (17) using Laplace transforms (see Appendix B)."
    \item line 625 Figure 3. The labels (a) (b) (c) (d) are missing in the graph
    \item line 728 equation (46) replace ``for" by ``with the choice of" as discussed for line 448
    \item line 1027 please use ``provided its crystalline structure is known."
    \item line 1139 Please replace equation (19) by equation (34).
\end{itemize}

\end{document}